Intended Table of Contents Thesis

### 2013-02-28 Chapters/Chapter1/literature_review.tex
Extend Literature Review

Other approaches form a higher level analyses of the raw data.
As used in \cite{barbivc2004segmenting}, the dimensionality of the data can be used to distinguish between actions.
Using Principal Component Analyses, Barbi{\v{c}} et al. use the dimensionality required to project the data points on a hyperplane while keeping the error below a certain rate as a measure of similarity.
The error threshold is fixed as a range of three times the standard deviation from the mean of the error.
In an extension of their method, using Probabilistic PCA \cite{tipping1999probabilistic}, the Mahanalobis distance \cite{duda1995pattern} for each frame represents similarity of concurrent motions.
In a third method the authors use a Gaussian Mixture Model *** elaborate on this one ***.
With the PPCA method the authors where able to get the best results, with precision of 92\% and recall of 95\%.
The test subjects wore 14 sensors on joints of the body and each frame is represented as a 56-dimensional vector.

>>>>

Other approaches form a higher level analyses of the raw data.
As used in \cite{barbivc2004segmenting}, the dimensionality of the data can be used to distinguish between actions.
Using Principal Component Analyses, Barbi{\v{c}} et al. use the dimensionality required to project the data points on a hyperplane while keeping the error below a certain rate as a measure of similarity.
The error threshold is fixed as a range of three times the standard deviation from the mean of the error.
In an extension of their method, using Probabilistic PCA \cite{tipping1999probabilistic}, the Mahanalobis distance \cite{duda1995pattern} for each frame represents similarity of concurrent motions.
By traversing the Mahanalobis distance as a function of the frames, cut-points are placed on specific points of interest.
*** NOTE to self: thus this method can segment (and group) unknown and new activities? ***
In a third method the authors use a Gaussian Mixture Model *** elaborate on this one [does it segment of direct classify?] ***.
Using this segmenting, and comparing the segments with earlier gathered representations of motions, the PPCA method gets the best results, with precision of 92\% and recall of 95\%.
The test subjects wore 14 sensors on joints of the body and each frame is represented as a 56-dimensional vector.
The test considered seven simple human motions: walking, running, sitting down, forward jumping, climbing, arm stretching and punching.
